---
title: "Auto Insurance"
subtitle: "Example R Studio project for training course"
author: 
  name: "Allan Engelhardt"
  company: "www.cybaea.net"
  gplus: "https://plus.google.com/+AllanEngelhardt"
  twitter: "@wiknin"
  www: "http://www.cybaea.net/"
  github: "cybaea"
date: "31 October 2017"
rights: "Copyright 2017 CYBAEA Limited. All rights reserved."
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
```

# About this file

The code here is not intended to be taken seriously, though you could extend it to a serious analysis (suggested homework!). The point here is to have some analysis that form the basis for our collaboration.

# Swedish Auto Insurance data

This document examines a classic data set. This dataset contains motor insurance data collected in 1977 in Sweden by the Swedish Committee on the Analysis of Risk Premium. Records contains individuals characteristics in addition to claim counts and severities.

```{r data}
suppressPackageStartupMessages( library("CASdatasets") )
data("swautoins", package = "CASdatasets")
```

```{r print-data}
swautoins
```


## Data description

The data give details of third party motor insurance claims in Sweden for the year 1977.

In Sweden all motor insurance companies apply identical risk arguments to classify customers, and thus their portfolios and their claims statistics can be combined. The data were compiled by a Swedish Committee on the Analysis of Risk Premium in Motor Insurance. The Committee was asked to look into the problem of analysing the real influence on claims of the risk arguments and to compare this structure with the actual tariff.

The variables are described below.

	
Kilometres  Kilometres travelled per year
----------	-----------------------------
1           < 1000
2           1000-15000
3           15000-20000
4           20000-25000
5           > 25000


Zone  Geographical zone
----  -----------------
1     Stockholm, Goteborg, Malmo with surroundings
2     Other large cities with surroundings
3     Smaller cities with surroundings in southern Sweden
4     Rural areas in southern Sweden
5     Smaller cities with surroundings in northern Sweden
6     Rural areas in northern Sweden
7     Gotland


- **Bonus**: 		No claims bonus. Equal to the number of years, plus one, since last claim
- **Make**: 		1-8 represent eight different common car models. All other models are combined - in class 9
- **Insured**: 		Number of insured in policy-years
- **Claims**: 		Number of claims
- **Payment**: 		Total value of payments in Skr
	

Make 4 is the Volkswagen 1200, which was discontinued shortly after 1977. The other makes could not be identified because of the potential for the data to impact on sales of those cars.

## Data preprocessing

We process the data to convert the rating factors from integers to categorical values with reasonable labels. We keep all as un-ordered factors to make the interpretation of the models easier.

```{r pre-process}
library("stringr")

swautoins <- swautoins %>%
  mutate(Kilometres = 
           factor(Kilometres, 
                  levels = 1:5,
                  labels = c("0-1000", "1000-15000", "15000-20000", 
                             "20000-25000", "25000-"),
                  ordered = FALSE),
         Zone = factor(Zone, levels = 1:7, labels = LETTERS[1:7], ordered = FALSE),
         Bonus = factor(Bonus, levels = 1:7, labels = str_c(1:7, " year"), ordered = FALSE),
         Make = factor(Make, levels = 1:9, labels = str_c("M", 1:9), ordered = FALSE),
         Payment = as.double(Payment)) %>%
  as.tibble()
```

```{r}
glimpse(swautoins)
```

```{r}
swautoins
```

Summary of the data:

```{r}
summary(swautoins)
```

# Frequency model

We use a Poisson distribution for our link function without checking it, which is not good practice! XXX Please fix this!

```{r frequency_model}
frequency_model <-
  glm(Claims ~ Kilometres + Zone + Bonus + Make + offset(log(Insured)),
      data = swautoins, family = poisson)
summary(frequency_model)
```

The coefficients on the natural scale are

```{r freq_rels}
rels <- coef(frequency_model)
rels <- exp( rels[1] + rels[-1] ) / exp( rels[1] )
rels
```


# Severity model

We will use a Gamma distribution here, again without checking it which is even worse practice than for the frequency models. XXX Please fix this code!

```{r severity_model}
severity_model <-
  glm(Payment ~ Kilometres + Zone + Bonus + Make,
      data = filter(swautoins, Payment > 0), family = Gamma, weights = Claims)
summary(severity_model)
```

# Conclusions

XXX Complete me!

# See Also

For more Insurance Pricing examples in R, try

- [R code for Chapter 1 of Non-Life Insurance Pricing with GLM](http://www.cybaea.net/Journal/2012/03/01/R-code-for-Chapter-1-of-Non_Life-Insurance-Pricing-with-GLM/)
- [R code for Chapter 2 of Non-Life Insurance Pricing with GLM](http://www.cybaea.net/Journal/2012/03/13/R-code-for-Chapter-2-of-Non_Life-Insurance-Pricing-with-GLM/)

You may also be interested in

- [Insurance Analytics and Pricing using R training course from CYBAEA](http://www.cybaea.net/Training/Insurance-Pricing-using-R/)
